### 2016-01-21 ARTICLES/RR/rapport/formalism.tex
rapport Helene 21/01/2016

\noindent \textbf{Definitions}
%\begin{mydef}
\begin{itemize}
\item \textit{A computation domain $D$ is a subpart  a mesh entities group, $D \subset E \in \mathcal{E}$.
\item The set of computation domains of a numerical simulation is denoted $\mathcal{D}$.
\item A neighborhood $n$ is a function which for a given entity $e \in E_i$, returns a set of $m$ entities in $E_j$, $n : E_i \rightarrow E_j^m$. One can notice that $i = j$ is possible.
\item The set of neihborhood functions in a numerical simulation is denoted $\mathcal{N}$.
\item A single data is written during a computation and is denoted $w \in \Delta$. Thus, the computation domain of the computation is $D \subset E_w=entity(w)$.
\item A set of data to read and use in a computation is denoted $R$. Each element of $R$ is a tuple $(r,n)$, where $r \in \Delta$ and $n$ is a neighborhood function such that $n : E_w \rightarrow entity(r)^m$. The neighborhood indicates which entities, on which $r$ is applied, will be read during the computation.
\item A numerical expression $\text{exp}_{w}: entity(w) \times R^n \rightarrow V_{w}$ is a function that computes the value of the written quantity $w \in \Delta$ for a given entity $e \in entity(w)=E_w$, using a set of input data $R$.
\item A computation kernel $k$ of a numerical simulation is defined as $c(R,w,\text{exp},D)$, where $R$ is the set of data read, $w \in \Delta$ is the unique data written, $\text{exp}$ is a numerical expression, and $D \in \mathcal{D}$ is the computation domain.}
\end{itemize}
%\end{mydef}
%If the number of computations in $\Gamma$ is $card(\Gamma)=n$, such that $\bigcup_{i=0}^{n-1}c_i = \Gamma$, then $\bigcup_{i=0}^{m-1}R_i \cup w_i \subseteq \Delta$.

>>>>

\noindent \textbf{Definitions}
%\begin{mydef}
\begin{itemize}
\item \textit{A computation domain $D$ is a subpart  a mesh entities group, $D \subset E \in \mathcal{E}$.
\item The set of computation domains of a numerical simulation is denoted $\mathcal{D}$.
\item A neighborhood $n$ is a function which for a given entity $e \in E_i$, returns a set of $m$ entities in $E_j$, $n : E_i \rightarrow E_j^m$. One can notice that $i = j$ is possible.
\item The set of neihborhood functions in a numerical simulation is denoted $\mathcal{N}$.
\item A single data is written during a computation and is denoted $w \in \Delta$. Thus, the computation domain of the computation is $D \subset E_w=entity(w)$.
\item A set of data to read and use in a computation is denoted $R$. Each element of $R$ is a tuple $(r,n)$, where $r \in \Delta$ and $n$ is a neighborhood function such that $n : E_w \rightarrow entity(r)^m$. The neighborhood indicates which entities, on which $r$ is applied, will be read during the computation.
\item A numerical expression $\text{exp}_{w}: entity(w) \times R^n \rightarrow V_{w}$ is a function which computes the values of the written quantity $w \in \Delta$ for a given entity $e \in entity(w)=E_w$, using a set of input data $R$.
\item A computation kernel $k$ of a numerical simulation is defined as $c(R,w,\text{exp},D)$, where $R$ is the set of data read, $w \in \Delta$ is the unique data written, $\text{exp}$ is a numerical expression, and $D \in \mathcal{D}$ is the computation domain.}
\end{itemize}
%\end{mydef}
%If the number of computations in $\Gamma$ is $card(\Gamma)=n$, such that $\bigcup_{i=0}^{n-1}c_i = \Gamma$, then $\bigcup_{i=0}^{m-1}R_i \cup w_i \subseteq \Delta$.
